---
title: "Plot Remi's Simulations"
author: "Royal T Booker"
date: "November 27, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Plotting Remi's simulations



```{r cars, echo=FALSE}
rm(list = ls())
library(ggplot2)
library(stringr)	
library(RColorBrewer)
library(ggthemes)
```


```{r pressure, echo=FALSE}
## Call the dataframe remi, just to be kewl
remi_raw <- read.csv('/media/booker/KingBolete/work/GeneticRescue/simulations/mean.SuperSet.summary.csv.gz')
str( remi_raw )
```

That's a whole lot of data, so let's slice it up a bit to make things quicker...

Let's ignore the Maladapted climate (MAC) alleles for the time being.

Let's also ignore pulsed migration for now.

Let's plot the Ne = 10000 simulations.

```{r slicer, echo=FALSE}

remi <- remi_raw[remi_raw$nbLoci_PAC == 0,]

remi$selScenario <-  paste(remi$S_OD, remi$nbLoci_OD, sep = '; ')

remi <- remi[str_count(remi$migration_scenario, ',') == 1,]

remi_noMAC <- remi[ remi$nbLoci_MAC == 0, ]

remi_MAC <- remi[ remi$nbLoci_MAC > 0, ] 

#remi_noMAC_PAC_0.05 <-remi_noMAC[remi_noMAC$fit_PAC ==  '1 0.99 0.98',]

```

# No pre-adapted climate (PAC) alleles
```{r xxx, echo=FALSE}

levels(as.factor(remi$nbLoci_OD))

noMAC_N10000 <- ggplot(data = remi_noMAC[remi_noMAC$N == 10000,], aes(x = Generation, y = relFitness, col = selScenario))+
  geom_hline(aes(yintercept = 1.0 ), alpha = 0.6, lty = 2)+
  geom_line()+
  ggtitle("noMAC;  N = 10000")+
scale_colour_brewer(expression(s[OD]*'; # Loci'), palette = "Paired")+
  facet_grid( migration_scenario ~ fit_PAC)+
  scale_y_continuous('Relative Fitness', limits = c(0.9, 1.05))+
  theme_bw()


noMAC_N10000_var <- ggplot(data = remi_noMAC[remi_noMAC$N == 10000,], aes(x = Generation, y = P0_varFit, col = selScenario))+
  geom_line()+
  ggtitle("noMAC;  N = 10000")+
scale_colour_brewer(expression(s[OD]*'; # Loci'), palette = "Paired")+
  facet_grid( migration_scenario ~ fit_PAC)+
  scale_y_continuous('Variance in Fitness')+
  theme_bw()

pdf("noMAC_0PAC_N10000_relFit.pdf", width = 6, height = 8)
print(noMAC_N10000)
dev.off()

pdf("noMAC_0PAC_N10000_varFit.pdf", width = 6, height = 8)
print(noMAC_N10000_var)
dev.off()

print(noMAC_N10000)
print(noMAC_N10000_var)

```


scale_colour_brewer(palette = "Paired")

# 5 pre-adapted climate (PAC) alleles

```{r slicer2, echo=FALSE}

remi <- remi_raw[remi_raw$nbLoci_PAC == 5,]

remi$selScenario <-  paste(remi$S_OD, remi$nbLoci_OD, sep = '; ')

remi <- remi[str_count(remi$migration_scenario, ',') == 1,]

remi_noMAC <- remi[ remi$nbLoci_MAC == 0, ]

remi_MAC <- remi[ remi$nbLoci_MAC > 0, ] 

#remi_noMAC_PAC_0.05 <-remi_noMAC[remi_noMAC$fit_PAC ==  '1 0.99 0.98',]

```



```{r xxx2, echo=FALSE}
levels(as.factor(remi$nbLoci_OD))

noMAC_N10000 <- ggplot(data = remi_noMAC[remi_noMAC$N == 10000,], aes(x = Generation, y = relFitness, col = selScenario))+
  geom_hline(aes(yintercept = 1.0 ), alpha = 0.6, lty = 2)+
  geom_line()+
  ggtitle("0 MAC; 5 PAC; N = 10000")+
scale_colour_brewer(expression(s[OD]*'; # Loci'), palette = "Paired")+
  facet_grid( migration_scenario ~ fit_PAC)+
  scale_y_continuous('Relative Fitness')+
  theme_bw()

noMAC_N10000_var <- ggplot(data = remi_noMAC[remi_noMAC$N == 10000,], aes(x = Generation, y = P0_varFit, col = selScenario))+
  geom_line()+
  ggtitle("0 MAC; 5 PAC; N = 10000")+
scale_colour_brewer(expression(s[OD]*'; # Loci'), palette = "Paired")+
  facet_grid( migration_scenario ~ fit_PAC)+
  scale_y_continuous('Variance in Fitness')+
  theme_bw()

pdf("noMAC_5PAC_N10000_relFit_5alleles.pdf", width = 6, height = 8)
print(noMAC_N10000)
dev.off()

pdf("noMAC_5PAC_N10000_varFit_5alleles.pdf", width = 6, height = 8)
print(noMAC_N10000_var)
dev.off()

print(noMAC_N10000)
print(noMAC_N10000_var)

```



# 50 pre-adapted climate (PAC) alleles


```{r slicer3, echo=FALSE}

remi <- remi_raw[remi_raw$nbLoci_PAC == 50,]

remi$selScenario <-  paste(remi$S_OD, remi$nbLoci_OD, sep = '; ')

remi <- remi[str_count(remi$migration_scenario, ',') == 1,]

remi_noMAC <- remi[ remi$nbLoci_MAC == 0, ]

remi_MAC <- remi[ remi$nbLoci_MAC > 0, ] 

#remi_noMAC_PAC_0.05 <-remi_noMAC[remi_noMAC$fit_PAC ==  '1 0.99 0.98',]

```



```{r xxx3, echo=FALSE}
levels(as.factor(remi$nbLoci_OD))

noMAC_N10000 <- ggplot(data = remi_noMAC[remi_noMAC$N == 10000,], aes(x = Generation, y = relFitness, col = selScenario))+
  geom_hline(aes(yintercept = 1.0 ), alpha = 0.6, lty = 2)+
  geom_line()+
  ggtitle("0 MAC; 50 PAC; N = 10000")+
scale_colour_brewer(expression(s[OD]*'; # Loci'), palette = "Paired")+
  facet_grid( migration_scenario ~ fit_PAC)+
  scale_y_continuous('Relative Fitness')+
  theme_bw()


noMAC_N10000_var <- ggplot(data = remi_noMAC[remi_noMAC$N == 10000,], aes(x = Generation, y = P0_varFit, col = selScenario))+
  geom_line()+
  ggtitle("0 MAC; 50 PAC; N = 10000")+
scale_colour_brewer(expression(s[OD]*'; # Loci'), palette = "Paired")+
  facet_grid( migration_scenario ~ fit_PAC)+
  scale_y_continuous('Variance in Fitness')+
  theme_bw()

pdf("noMAC_50PAC_N10000_relFit_50alleles.pdf", width = 6, height = 8)
print(noMAC_N10000)
dev.off()

pdf("noMAC_50PAC_N10000_varFit_50alleles.pdf", width = 6, height = 8)
print(noMAC_N10000_var)
dev.off()
print(noMAC_N10000)
print(noMAC_N10000_var)

```


# 5 Maladapted climate alleles; 0 PAC alleles

```{r slicer4, echo=FALSE}

remi <- remi_raw[remi_raw$nbLoci_PAC == 0,]

remi$selScenario <-  paste(remi$S_OD, remi$nbLoci_OD, sep = '; ')

remi <- remi[str_count(remi$migration_scenario, ',') == 1,]

remi_noMAC <- remi[ remi$nbLoci_MAC == 5, ]

remi_MAC <- remi[ remi$nbLoci_MAC > 0, ] 

#remi_noMAC_PAC_0.05 <-remi_noMAC[remi_noMAC$fit_PAC ==  '1 0.99 0.98',]

```



```{r xxx4, echo=FALSE}
levels(as.factor(remi$nbLoci_OD))

noMAC_N10000 <- ggplot(data = remi_noMAC[remi_noMAC$N == 10000,], aes(x = Generation, y = relFitness, col = selScenario))+
  geom_hline(aes(yintercept = 1.0 ), alpha = 0.6, lty = 2)+
  geom_line()+
  ggtitle("5 MAC; 0 PAC; N = 10000")+
scale_colour_brewer(expression(s[OD]*'; # Loci'), palette = "Paired")+
  facet_grid( migration_scenario ~ fit_PAC)+
  scale_y_continuous('Relative Fitness')+
  theme_bw()


noMAC_N10000_var <- ggplot(data = remi_noMAC[remi_noMAC$N == 10000,], aes(x = Generation, y = P0_varFit, col = selScenario))+
  geom_line()+
  ggtitle("5 MAC; 0 PAC; N = 10000")+
scale_colour_brewer(expression(s[OD]*'; # Loci'), palette = "Paired")+
  facet_grid( migration_scenario ~ fit_PAC)+
  scale_y_continuous('Variance in Fitness')+
  theme_bw()

pdf("5MAC_0PAC_N10000_relFit_5alleles.pdf", width = 6, height = 8)
print(noMAC_N10000)
dev.off()

pdf("5MAC_0PAC_N10000_varFit_5alleles.pdf", width = 6, height = 8)
print(noMAC_N10000_var)
dev.off()
print(noMAC_N10000)
print(noMAC_N10000_var)

```


```{r slicer5, echo=FALSE}

remi <- remi_raw[remi_raw$nbLoci_PAC == 5,]

remi$selScenario <-  paste(remi$S_OD, remi$nbLoci_OD, sep = '; ')

remi <- remi[str_count(remi$migration_scenario, ',') == 1,]

remi_noMAC <- remi[ remi$nbLoci_MAC == 5, ]

remi_MAC <- remi[ remi$nbLoci_MAC > 0, ] 

#remi_noMAC_PAC_0.05 <-remi_noMAC[remi_noMAC$fit_PAC ==  '1 0.99 0.98',]

```

# 5 Maladapted climate alleles; 5 PAC alleles


```{r xxx5, echo=FALSE}
levels(as.factor(remi$nbLoci_OD))

noMAC_N10000 <- ggplot(data = remi_noMAC[remi_noMAC$N == 10000,], aes(x = Generation, y = relFitness, col = selScenario))+
  geom_hline(aes(yintercept = 1.0 ), alpha = 0.6, lty = 2)+
  geom_line()+
  ggtitle("5 MAC; 5 PAC; PAC = 0.05; N = 10000")+
scale_colour_brewer(expression(s[OD]*'; # Loci'), palette = "Paired")+
  facet_grid( migration_scenario ~ fit_PAC)+
  scale_y_continuous('Relative Fitness')+
  theme_bw()


noMAC_N10000_var <- ggplot(data = remi_noMAC[remi_noMAC$N == 10000,], aes(x = Generation, y = P0_varFit, col = selScenario))+
  geom_line()+
  ggtitle("5 MAC; 5 PAC; PAC = 0.05; N = 10000")+
scale_colour_brewer(expression(s[OD]*'; # Loci'), palette = "Paired")+
  facet_grid( migration_scenario ~ fit_PAC)+
  scale_y_continuous('Variance in Fitness')+
  theme_bw()

pdf("5MAC_5PAC_N10000_relFit_5alleles.pdf", width = 6, height = 8)
print(noMAC_N10000)
dev.off()

pdf("5MAC_5PAC_N10000_varFit_5alleles.pdf", width = 6, height = 8)
print(noMAC_N10000_var)
dev.off()
print(noMAC_N10000)
print(noMAC_N10000_var)

```
